A Systematic Approach to Model Predictive Controller Constraint Handling: Rigorous Geometric Methods

### 2011-04-29 article.tex
- minor fixes [article.tex article_extfig.tex] - journal abreviations in articlerefs.bib

\usepackage{tikz}
\usepackage{pgfplots}
%TODO - remove \usepackage (convert images to pdf/eps)

@@

A rigorous and systematic approach to constraint management is proposed, building on the work of \citet{vinsonartoi} in interpreting constraint interactions. 
The method focuses on linear steady-state system models, and provides routines to obtain the following information: effects of constraint changes on the corresponding input or output constraints, feasibility checks for constraints, constraint-type information, specification of constraint-set size and optimal fitting of constraints within the desirable input or output space.

@@

\subsubsection{Constraints}\label{sec:mpccons}
Most commercial MPC packages allow only high and low limits to be imposed on outputs or inputs.
The only validation of these constraints are against an outermost constraint set, often referred to as 'Engineering Limits'.
This set typically consists of physical limits on inputs and outputs, as well as limits that avoid damage to equipment.

@@

From this definition it is clear that the controlability of a process decreases if the DOS does not cover the whole AOS. 
Servo- and regulatory operability indices are also defined in the text, but are not shown here.

@@

The same argument for feasible constraints apply to setpoints.
The specification of setpoints should be checked to be within the attainable output space for a given available input space.

@@

\section{2$\times$2 Distillation Column Example}\label{sec:dist}
The method proposed in the preceding section is now illustrated for a practical system.
Even though the method applies to higher order systems, a $2 \times 2$ system is considered to ease graphical representation.
\subsection{Process Description}
The example case study is a 10-plate distillation column from the Process Modelling and Control laboratory of the University of Pretoria.
The column is run as a closed system with bottoms and distillate mixed and fed back into the column.
Figure~\ref{fig:columnpfd} shows a simplified process flow diagram of the column.
\begin{figure}[htbp]
  \centering
    %\includegraphics[width=8cm]{columnpfd.pdf}
    \scalebox{1}{\input{columnpfd}}
  \caption[Laboratory distillation column photo and flow diagram]{Laboratory distillation column flow diagram.}
  \label{fig:columnpfd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    %\includegraphics[width=8cm]{columnais.pdf}
    %\qquad
    %\includegraphics[width=8cm]{columnaos.pdf}
    %\includegraphics[width=8cm]{columnaosfocus.pdf}
    \scalebox{1}{\input{columnais}}
    \scalebox{1}{\input{columnaos}}
    \scalebox{1}{\input{columnaosfocus}}
  \caption{AIS (a), AOS and DOS (b), and AOS$\cap$DOS (c) showing a very small operating region.}
  \label{fig:columnaisaos}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    %\includegraphics[width=8cm]{columnfitbox.pdf}
    \scalebox{1}{\input{columnfitbox}}
  \caption[Fitted constraints for the laboratory distillation column]{Intersection of AOS and DOS with fitted high and low limits for the column tray temperatures.}
  \label{fig:columnfitbox}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \scalebox{1}{\input{columninputs}}
%    \includegraphics[width=8cm]{columninputs.pdf}
%    \includegraphics[width=8cm]{columninputszoom.pdf}
    \scalebox{1}{\input{columninputszoom}}
  \caption{Constraints in the input space for the column (a) and focus on the constraint changes showing input clamping (b).}
  \label{fig:columnconsinput}
\end{figure}

>>>>

@@

A rigorous and systematic approach to constraint management is proposed, building on the work of \citet{vinsonartoi} in interpreting constraint interactions. 
The method focuses on linear steady-state system models, and provides routines to obtain the following information: effects of constraint changes on the corresponding input or output constraints, feasibility checks for constraints and constraint-type information.

@@

\subsubsection{Constraints}\label{sec:mpccons}
Most commercial MPC packages allow only high and low limits to be imposed on outputs or inputs.
The only validation of these constraints is against an outermost constraint set, often referred to as 'Engineering Limits'.
This set typically consists of physical limits on inputs and outputs, as well as limits that avoid damage to equipment.

@@

From this definition it is clear that the operability of a process decreases if the DOS does not cover the whole AOS. 
Servo- and regulatory operability indices are also defined in the text, but are not shown here.

@@

The same argument for feasible constraints applies to setpoints.
The specification of setpoints should be checked to be within the attainable output space for a given available input space.

@@

\section{2$\times$2 Distillation Column Example}\label{sec:dist}
The method proposed in the preceding section is now illustrated for a practical system.
Even though the method applies to higher order systems, a $2 \times 2$ system is considered to ease graphical representation.
\subsection{Process Description}
The example case study is a 10-plate distillation column from the Process Modelling and Control laboratory of the University of Pretoria.
The column is run as a closed system with bottoms and distillate mixed and fed back into the column.
Figure~\ref{fig:columnpfd} shows a simplified process flow diagram of the column.
\begin{figure}[htbp]
  \centering
    \includegraphics{figure1.pdf}
  \caption[Laboratory distillation column photo and flow diagram]{Laboratory distillation column flow diagram.}
  \label{fig:columnpfd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics{figure2a.pdf}
    \includegraphics{figure2b.pdf}
    \includegraphics{figure2c.pdf}
  \caption{AIS (a), AOS and DOS (b), and AOS$\cap$DOS (c) showing a very small operating region.}
  \label{fig:columnaisaos}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics{figure3.pdf}
  \caption[Fitted constraints for the laboratory distillation column]{Intersection of AOS and DOS with fitted high and low limits for the column tray temperatures.}
  \label{fig:columnfitbox}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics{figure4a.pdf}
    \includegraphics{figure4b.pdf}
  \caption{Constraints in the input space for the column (a) and focus on the constraint changes showing input clamping (b).}
  \label{fig:columnconsinput}
\end{figure}
